Finite element analysis ofmulti-dimensional and simplifiedmodels for beams and plates

### 2023-11-16 files/Chapter3/femconvergence.tex
small fixes

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{FEM comparison of eigenvalues and eigenfunctions}

@@

Galerkin approximation for \eqref{GEVP}:
For $u^h \in S^h$ and $b(u^h, v) = \lambda^h(u^h,v)$ for all $v \in S^h$. For detail, see Chapter 5.

@@

\textbf{Rayleigh-Ritz Projection}\\
If $u \in V$, then $Pu$ is its component in the subspace $S^h$.
\begin{equation*}
	b(u-Pu,v^h) = 0 \ \text{ for all } v \in S^h.
\end{equation*}

>>>>

\documentclass[../../main.tex]{subfiles}
\begin{document}
\section{FEM computation of eigenvalues and eigenfunctions}

@@

Galerkin approximation for \eqref{GEVP}:

For $u^h \in S^h$ and $b(u^h, v) = \lambda^h(u^h,v)$ for all $v \in S^h$. For detail, see Chapter 5.

@@

\textbf{Rayleigh-Ritz Projection}\\
If $u \in V$, then $Pu$ is in the subspace $S^h$.
\begin{equation*}
	b(u-Pu,v^h) = 0 \ \text{ for all } v \in S^h.
\end{equation*}
